Revisiting the hydrodynamic modulation of short waves by longer waves

### 2024-09-19 paper/paper.tex
Begin work on wave groups
Update paper.tex

>>>>

We now proceed to examine the numerical solutions with the long-wave forcing
applied as a long-wave group.
The wave group is simulated as a non-dispersive train of long waves whose
amplitude scales with $\cos{2 \pi t / (N T_L)}$, where $N$ is the number of
long waves in the group.
The elevation of the long waves thus gradually ramps up from rest to $a_L$ at $t = N/2 T_L$, after which it gradually decreases toward zero.
In this simulation, $N = 10$ and $\varepsilon = 0.1$ as in the previous two simulations.
The modulations of short-wave wavenumber, amplitude, and steepness in response to such long-wave group is shown in Fig. \ref{fig:modulation_3panel_groups}.
Like in the case of a linear ramp, the modulation pattern here is locked in to the long-wave crest and peaks at approximately 1.2 for short-wave steepness.
After the peak of the long-wave group passes, the short-wave modulation recedes back toward the resting state.
